\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

The stochastic volatility model \citep{kim} is a very important class of models, because it fits time series data with random variability. This model has been studied through the classical point of view as through the Bayesian one. Nevertheless, its many specifications still needs an adequated solution.

The recent work of \cite{kastner} presented important developments of the Bayesian approach for the estimation of the model parameters. The authors introduce a very innovative idea called Ancillarity-Sufficiency Interweaving Strategy, which consists in switching the model's parametrization during the estimation process. However, the proposed estimation of the latent variable, which governs the model, is a bit tricky. So, the present work proposes an alternative way, also simpler, to estimate the latent variable of the process based on the work of \cite{mccormick}.

The methodologies proposed by the last two authors were adapted in this dissertation to suggest an alternative way to estimate the parameters of the stochastic volatility model. The effectiveness of the new proposal was evaluated by using simulated data. The emerging issues of the proposed procedure were highlighted and some new alternatives to solve them were suggested at the end of this work.
\newline

\noindent \textbf{Key Words}: \textit{Bayesian Statistics, Stochastic Volatility Models, Dynamic Linear Models, Ancillarity-Sufficiency Interweaving Strategy, JAGS}
